\documentclass[10pt, a4paper, sans]{moderncv}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.9]{geometry}
\usepackage[super]{nth}
\moderncvtheme[blue]{classic}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{fontawesome}
\firstname{Narayan}
\familyname{Acharya}
\title{}
\address{H1/7 Godrej HillSide Colony}{Vikhroli - 400079, Mumbai}
\mobile{+91 97690 95093}
\email{narayan.acharya6@gmail.com}

\AfterPreamble{\hypersetup{
		pdfauthor={Narayan Acharya},
		pdftitle={Resume for Narayan Acharya},
		pdfsubject={Detailed Resume for Narayan Acharya},
		pdftoolbar=true,
		pdfmenubar=true,
		pdfstartview={FitH},
		pdfkeywords={Resume, Narayan Acharya, Android, LiveFiesta, TechGenium, Engineering},
		pdfcreator={Narayan Acharya},
		pdfproducer={Narayan Acharya},
		bookmarks=false,
		colorlinks=false,
		urlcolor=black,
	}}


\begin{document}

\makecvtitle

\subsection{\hfil About Me \hfil}
I graduated from K.J Somaiya College of Engineering(K.J.S.C.E), Mumbai, B.E. in Information Technology with distinction. I have interests in \emph{Software Design \& Development}, \emph{Theoretical Computer Science} and \emph{Discrete Mathematics} and like to take online courses to learn new things during my free time. I stood \nth{923} among more than 1,00,000 applicants in GATE-CSE, 2015.

\section{Experience}
\cventry
{June '16 - Jan '17 \\ {\faAndroid} {\faUsers}}
{Lead Android Developer}
{LiveFiesta Pvt.Ltd.}
{Mumbai}
{}
{
{\faCaretRight} Designed and developed ready to deploy application with features like payment gateway integration, push notifications, deep linking, Google Analytics integration among various others. \\
{\faCaretRight} Leveraged MVP Architecture pattern along with design principles like single responsibility, dependency injection and others for clean, testable and maintainable code. \\
{\faCaretRight} Saved development time by mocking server responses to keep developing the application in parallel with the backend application server. Learnt to write automated unit and functional tests to save code refactor time. \\
{\faCaretRight} Designed initial version of the Android application using tools like Adobe Illustrator and Photoshop with UI/UX principles in mind. \\
{\faCaretRight} Actively involved in team building, interviewing candidates for design and technology and training new hires.\\
{\faCaretRight} Developed apps for in-house use for redeeming tickets at events and tracking delivery of physical tickets to customers.
}

\cventry
{June '15 - May '16 \\ {\faAndroid} {\faBriefcase}}
{Co-Founder \& Android Developer}
{TechGenium}
{Mumbai}
{}
{
{\faCaretRight} Helped build a technology services company from ground up that provided software solutions. \\
{\faCaretRight} Undertook project management responsibilities that included tasks like requirements analysis, project draft and proposal and tracking project timelines and deadlines. \\
{\faCaretRight} Designed and developed "Quizy", a simple quiz application. \\
{\faCaretRight} Helped interview candidates for various positions. Undertook training Android interns. \\
{\faCaretRight} Conducted a weekend course spanning 7 weeks to teach Android application development to students. This helped with getting potential interns for Android based projects.
}

\section{Publication(s)}
\cventry
{IJCA Publication 
\href{http://www.ijcaonline.org/archives/volume116/number14/20408-2766}{\faFile}}
{Visualization of Mechanics Problems based on
Natural Language Processing}
{K.J.S.C.E, Mumbai}
{}
{}
{}

\section{Academic \& Personal Projects}
\cventry
{Capstone Project \\ {\faGithub}}
{Visualization of Mechanics Problems based on
Natural Language Processing}
{}
{}
{}
{It gives insights to generating 3D models based on simple English language sentences, in this case Newtonian mechanics problems.\bfseries{(Java)}}

\cventry
{Home Automation Android App \\ {\faAndroid}}
{Android app to automate electrical appliances remotely}
{}
{}
{}
{This project was done in collaboration with students from Electronics department.Received \nth{1} prize in Sustainable Development in Prakalpa 2014-KJSCE.\bfseries{(Java)}}

\cventry
{CSI Android App \\ {\faAndroid}}
{Android app for CSI - KJSCE Chapter 2013-14}
{}
{}
{}
{Allows students to view events, team information and receive notifications.\bfseries{(Java)}}

\cventry
{Neowin Android App \\ {\faAndroid}}
{Android app to read news feeds from popular news website, \href{http://www.neowin.net/}{Neowin}}
{}
{}
{}
{Being an avid reader of Neowin and the lack of an official Android app at the time, led to this app.\bfseries{(Java)}}

%\cventry
%{Online Courses \\ {\faGlobe}}
%{Various courses on \href{http://www.coursera.org/}{Coursera}}
%{}
%{}
%{}
%{Successfully completed courses on Python, Game Development in %Python, Game Development in C\# and Android with weekly projects. %\bfseries{(Java, Python C\#)}}

\section{Technical Skills}
\cvitem
{\bfseries{Languages}}
{Java, Python, C, C++, C\#, SQL, HTML, CSS, JavaScript, \LaTeX{}}

\cvitem
{\bfseries{Frameworks}}
{Android, Flask, Bootstrap}

\cvitem
{\bfseries{Protocols/API}}
{XML, JSON, REST}

\cvitem
{\bfseries{Databases}}
{SQLite, MongoDB, MySQL, PostgreSQL}

\cvitem
{\bfseries{Tools}}
{Git, Android Studio, Adobe Photoshop, Adobe Illustrator}

\section{Education}
\cventry
{2011-2015}
{B.E. Information Technology}
{K.J.Somaiya College of Engg.}
{Mumbai}
{72.94\%}
{}

\cventry
{2009-2011}
{H.S.C}
{S.I.E.S College of Arts, Science and Commerce}
{Mumbai}
{84.33\%}
{}

\cventry
{2009}
{S.S.C}
{Gopal Sharma Memorial School}
{Mumbai}
{91.07\%}
{}

\end{document}